A Logistic Regression Approach to CoIL Challenge 2000

### 2019-11-11 final project/Manuscript.Rmd
More work on final project

<!--Discuss how other researchers have addressed similar problems, what their achievements are, and what the advantage and drawbacks of each reviewed approach are. Explain how your investigation is similar or different to the state-of-theart. Please cite the relevant papers where appropriate.-->

@@

The maximum number of policyowners that could be found was 238.  The winning model [@Elkan] selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear!) policy owners. [@Putten]

>>>>

<!--Discuss how other researchers have addressed similar problems, what their achievements are, and what the advantage and drawbacks of each reviewed approach are. Explain how your investigation is similar or different to the state-of-the-art. Please cite the relevant papers where appropriate.-->

@@

```{r}
# Recreate the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121),
                                n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data=prediction_scores, aes(x=score, y=n)) +
  geom_bar(stat="identity") +
  xlab("Policy Owners") +
  ylab("Submissions") +
  xlim(37, 122) +
  ggtitle("Correct Predictions from CoIL 2000 Challenge Submissions")
```

The maximum number of policyowners that could be found was 238.  The submissions identified 95 policy owners on average.  The winning model [@Elkan] identified 121 policy owners.  Random selection results in identifying 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear) policy owners. [@Putten].

Our investigation is similar to @Doornik in that we used a LOGIT model. **Reproduce his model and describe the results**

### 2019-11-11 final project/Manuscript.tex
More work on final project

The maximum number of policyowners that could be found was 238. The winning model (Elkan, 2000) selected 121 policy owners. Random selection results in 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear!) policy owners. (Putten et al., 2000)

>>>>

\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}

The maximum number of policyowners that could be found was 238. The submissions identified 95 policy owners on average. The winning model (Elkan, 2000) identified 121 policy owners. Random selection results in identifying 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear) policy owners. (Putten et al., 2000).
